Injrury Outcomes - WHW matrices

### 2020-08-12 injury_tables.Rmd
Make link for direct download
Fix section

### Who hit whom matrix for all case cities as CSV {#whw_all_csv}

[View from](https://github.com/ITHIM/ITHIM-R/blob/master/results/multi_city/whw_matrices/whw_lng.csv)

>>>>

## Who hit whom matrix for all case cities as CSV {#whw_all_csv}

[Download from](https://raw.githubusercontent.com/ITHIM/ITHIM-R/master/results/multi_city/whw_matrices/whw_lng.csv)
